Graph-Based Neural Reconstruction from Morphological Skeletons

### 2017-11-15 papers/cvpr2018/2_method.tex
paper: updated figures with better meshes and created ROC curve

\begin{figure}[t]
	\centering
	\includegraphics[width=0.92\linewidth]{./figures/skeleton1.png}
	\includegraphics[width=0.92\linewidth]{./figures/skeleton2.png}
	\caption{Example skeletons (in white) extracted from segments (blue and green) using the TEASER algorithm.}
	\label{fig:skeletonization}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.92\linewidth]{./figures/split_error1.png}
	\includegraphics[width=0.92\linewidth]{./figures/split_error2.png}
	\caption{Two erroneously split segments. \hp{split in top figure impossible to see - use brighter colors. both figures are too dark - increase brightness of segments}}
	\label{fig:merge_candidates}
\end{figure}

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=0.92\linewidth]{./figures/skeleton1.png}
	\includegraphics[width=0.92\linewidth]{./figures/skeleton2.png}
	\caption{Example skeletons (in black) extracted from segments (blue and green) using the TEASER algorithm.}
	\label{fig:skeletonization}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.92\linewidth]{./figures/split_error1.png}
	\includegraphics[width=0.92\linewidth]{./figures/split_error2.png}
	\caption{Two erroneously split segments.}
	\label{fig:merge_candidates}
\end{figure}
